### 2020-07-09 steadystate.tex
decay heat sections

\section{Decay Heat}

The inclusion of a decay heat model effectively redistributes a fraction of
the volumetric heat source from the center of the core to the entire loop.
Thus, there should be a slight flattening of the temperature distribution
across the entire primary loop.

>>>>

\clearpage

\section{Steady-State Decay Heat Results}

The movement of decay heat precursors effectively redistributes a fraction of
the volumetric heat source concentrated at the center of the core to the
entire primary loop.
Thus, the temperature distribution in the core should
show less extreme temperatures compared with the simulation without decay
heat.

Figure \ref{fig:decayheat} shows the decay heat source distribution in the
core for groups 1 to 3. The decay constants are $\lambda_j = 0.197$ s$^{-1},
0.0168$ s$^{-1}, 0.000358$ s$^{-1}$ for groups 1, 2, and 3, respectively.
Similar to the delayed neutron precursor distributions, the shorter-lived
decay heat precursors show greater build-up in the recirculation zones
compared with the longer-lived decay heat precursors that are more evenly
distributed throughout the core.

\begin{figure}[htbp!]
    \centering
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{heat1}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{heat2}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{heat3}
    \end{subfigure}
    \caption{Decay heat source distribution in the core for decay heat groups
    1 to 3 (from left to right). Refer to Figure \ref{fig:decayheattemp} for
    the height and radius scales on the y and x axes, respectively. Note the
    different scales for each distribution.}
    \label{fig:decayheat}
\end{figure}

Figure \ref{fig:decayheattemp} shows the
difference in core temperatures at steady state with decay heat modeling
relative to the core temperatures without decay heat in Figure
\ref{fig:flow-temp}. This figure uses a different colormap scheme to clearly
distinguish between temperature increases and decreases in the core. The
hotspots in the recirculation zones are approximately
2 to 4 K cooler, while the cooled salt flowing in from the inlet is
approximately 2 K hotter. These regions correspond to the hottest and coldest
areas in the core and the results agree with the expectation that the extreme
temperatures would be affected the most by the introduction of decay heat
precursors. The difference between the outlet and inlet temperatures falls
from 101.1 K to 98.9 K as some of the decay heat precursors deposit heat in
the outer loop region. The figure also shows some unphysical oscillations in
the temperature near the outlet because the mesh near the boundary is too
coarse. Users can avoid these oscillations near the outlet but using a mesh
that is progressively finer the closer the element is to the boundary. The
present author did not resolve this issue due to time constraints.

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.6\textwidth]{decay-heat-temp}
    \caption{Difference in core temperatures at steady state with decay heat
    relative to the result without decay heat (Figure \ref{fig:flow-temp}).}
    \label{fig:decayheattemp}
\end{figure}

### 2020-07-09 transient.tex
decay heat sections

\subsection{Without Decay Heat}

@@

>>>>

\subsection{Without Decay Heat} \label{sec:wodecayheat}

@@

Decay heat from fission products poses a great safety risk in a loss of
heat sink accident. Section \ref{sec:wodecayheat} showed that prompt fission
power output quickly falls as core temperatures rise. However, decay power
output is independent of the instantaneous neutron flux. Figure
\ref{fig:moltresdecaypower} shows that the decay power output remains
relatively high during a short-term transient. Decay heat becomes the dominant
heat source from $t=34$ s and falls at a much slower rate than prompt heat.
Figure \ref{fig:moltresdecaytemp} highlights the
greater core temperature increase attributed to decay heat as compared with
the results without decay heat. By $t=120$ s, the model with decay heat
records an average core temperature increase that is 45 K higher than the
model without decay heat. The average core temperature reaches approximately
1220 K and would continue to rise further. This places undue thermal stress
and accelerate corrosion rates in the Hastelloy structural material. In the
absence of an auxiliary heat removal system in the primary loop, reactor
operators would have to rely on the freeze plug to drain the core into a drain
tank with emergency cooling systems to keep the salt cool.

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.85\textwidth]{moltres-decay-power}
    \caption{Power output during
    an unprotected loss of heat sink transient in the Moltres model with and
    without decay heat.}
    \label{fig:moltresdecaypower}
    \includegraphics[width=.85\textwidth]{moltres-decay-temp}
    \caption{Average core temperature increase during
    an unprotected loss of heat sink transient in the Moltres model with and
    without decay heat.}
    \label{fig:moltresdecaytemp}
\end{figure}

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.85\textwidth]{decay-temp}
    \caption{Loop-averaged temperature increase during
    an unprotected loss of heat sink transient in the Moltres and Polimi
    models \cite{fiorina_modelling_2014} with decay heat.}
    \label{fig:polimidecaytemp}
\end{figure}

Figure \ref{fig:polimidecaytemp} shows the loop-averaged temperature
increase in the Moltres and Polimi models \cite{fiorina_modelling_2014}. The
TUDelft model does not have a decay heat modeling capability. The Moltres
model predicts the same increasing trend in the temperature. The loop-averaged
temperature rises significantly at the start of the transient and continues to
rise at a decreasing rate. The loop-averaged temperature increase in the
Moltres model at $t=120$ s is approximately 17 K lower than that in the Polimi
model. It is difficult to ascertain the exact cause for this difference
without the power profile from the Polimi model with decay heat to compare
with. However, if the decay power output are similar, the stronger negative
temperature reactivity coefficient would cause the prompt power output in the
Moltres model to fall faster than the Polimi model. Consequently, the
loop-averaged temperature would be lower as shown in the figure. Overall, the
results for the loss of heat sink transient agree with the Polimi and TUDelft
model results in both cases, with and without decay heat modeling.
